Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-23 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-23 22-26-09

For example, as the panel $p$ in Table~\ref{tab:NumofModules} $Loss-rate(p,Q_{1},Q_{2})=0$, $Loss-rate(p,Q_{1},Q_{3})=0.5$, that is, for target current level $Q_{1}$ there is no ``$loss$'' for current level $Q_{2}$ and only loss ``0.5'' active module for current level $Q_{3}$.

To assign panels of target current level $n$ to $n$-th string, the following step are applied.
Let $m$ be the required number of active modules per-string.
\begin{enumerate}
\item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
\item\label{step:2} Selects sorted panels one by one until reaching the required number of active modules $m$.
  In step 2, panel with no active modules is skipped.
\item\label{step:3} Optimize the number of active modules.
  In step 3, if the number of selected active modules exceeds the required number $m$, redundant panels will be removed if exist.
\end{enumerate}

\subsection{Algorithm}\label{sec:algorithm}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.

>>>>

For example, as the panel $p$ in Table~\ref{tab:NumofModules} $Loss-rate(p,Q_{1},Q_{2})=0$, $Loss-rate(p,Q_{1},Q_{3})=0.5$, that is, for target current level $Q_{1}$ there is no ``$losses$'' for current level $Q_{2}$ and only ``$loss$'' 0.5 active module for current level $Q_{3}$.

To assign panels of target current level $n$ to $n$-th string, the following step are applied.
Let $m$ be the required number of active modules per-string.
\begin{enumerate}
  \item\label{step:1} Sort un-selected panels with ``$loss$'' and ``$gain$''.
% \item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
\item\label{step:2} Selects sorted panels one by one until reaching the required number of active modules $m$.
  % In step 2, panel with no active modules is skipped.
\item\label{step:3} Optimize the number of active modules.
  In step 3, if the number of selected active modules exceeds the required number $m$, redundant panels will be removed if exist.
\end{enumerate}
% \begin{table*}[h]
%   \caption[]{ \label{tab:Exampleofalgo}}
%   \centerline{EXAMPLE OF PROPOSED ALGORITHM}
%   \vskip5pt
%   \centering
%   \begin{tabular}{c|c|l|ccccccc}
%     \hline
%     \hline
%     \multicolumn{3}{c|}{\multirow{2}{*}{}}                                    & \multicolumn{7}{c}{Panels}                                                      \\ \cline{4-10} 
% \multicolumn{3}{c|}{}                                                     & P1  & P4  & P5                       & P2 & P3 & P7                     & P6     \\ \hline
% \multirow{3}{*}{Current Levels} & Q1 & \multirow{3}{*}{Number of modules} & 2   & 2   & 2                        & 1  & 1  & 1                      & 0      \\ \cline{2-2}
%                                 & Q2 &                                    & 2   & 2   & 2                        & 1  & 1  & 1                      & 1      \\ \cline{2-2}
%                                 & Q3 &                                    & 3   & 3   & 3                        & 2  & 2  & 2                      & 2      \\ \hline
% \multirow{2}{*}{Loss-rate}      & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q2)} & 0   & 0   & \multicolumn{1}{c|}{0}   & 0  & 0  & \multicolumn{1}{c|}{0} & $\infty$ \\ \cline{2-3}
%                                 & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q3)} & 0.5 & 0.5 & \multicolumn{1}{c|}{0.5} & 1  & 1  & \multicolumn{1}{c|}{1} & 1      \\ \hline
% \multicolumn{3}{c|}{Algorithm  priority}                                  & 1   & 2   & 3                        & 4  & 5  & 6                      & 7      \\ \hline
% \end{tabular}
% \end{table*}

As shown in Table~\ref{tab:exampleofalgo} ,there is an example that demonstrate how to select PV panel for a string on current level $Q_{1}$ where required active module per string $m$ is 4.
Panels are sorted by $Loss-rate$ which seen as ``$loss$'' and $M_{p}(Q_{1})$ which seen as ``$gain$''.
In this example, panel P1, P4 and P5 have the same $Loss-rate$ is (0, 0.5) which is smaller than other panels.
Thus, those three panels are grouped into the \textbf{First} ``$loss$'' level.
Similarly, panel P2, P3, and P7 are in the \textbf{Second} ``$loss$'' level and panel p6is in the \textbf{last} ``$loss$'' level because it does not contain any module that is able to activate on the target current level.
Panel selection started from the \textbf{First} ``$loss$'' level, after selected panels active PV modules exceed $m$ ($m=4$ in this example) selection procedure will terminate.
If some redundant panels exist, those panels are removed.
In this example, no redundant panel exist and panel P1 and P4 are selected for target current level $Q_{1}$ PV string.
\begin{table}[htbp]
  \caption[]{\label{tab:exampleofalgo}}
  \centerline{EXAMPLE OF PROPOSED ALGORITHM}
  \vskip5pt
  \begin{tabular}{c|c|ccccccc}
  \hline
  \hline
\multicolumn{2}{c|}{\multirow{2}{*}{}}  & \multicolumn{7}{c}{Panels}                                                      \\ \cline{3-9} 
\multicolumn{2}{c|}{}                   & P1  & P4  & P5                       & P2 & P3 & P7                     & P6     \\ \hline
\multirow{3}{*}{Number of modules} & Q1 & 2   & 2   & 2                        & 1  & 1  & 1                      & 0      \\ \cline{2-2}
                                   & Q2 & 2   & 2   & 2                        & 1  & 1  & 1                      & 1      \\ \cline{2-2}
                                   & Q3 & 3   & 3   & 3                        & 2  & 2  & 2                      & 2      \\ \hline
\multicolumn{2}{c|}{Loss-rate(p,Q1,Q2)} & 0   & 0   & \multicolumn{1}{c|}{0}   & 0  & 0  & \multicolumn{1}{c|}{0} & $\infty$ \\ \cline{1-2}
\multicolumn{2}{c|}{Loss-rate(p,Q1,Q3)} & 0.5 & 0.5 & \multicolumn{1}{c|}{0.5} & 1  & 1  & \multicolumn{1}{c|}{1} & 1      \\ \hline
\multicolumn{2}{c|}{Priority}           & 1   & 2   & 3                        & 4  & 5  & 6                      & 7      \\ \hline
\end{tabular}
\end{table}
\subsection{Algorithm}\label{sec:algorithm}
Proposed algorithm assigns PV panels of given configuration in order of target current level $Q_{1}, Q_{2},\dots, Q_{s}$.
Where $Q_{i}\geq Q_{j}$ ($i \leq j$) holds for configurations current sequence $Q = (Q_{1},Q_{2},\dots,Q_{s})$.
Pseudo code of proposed algorithm as shown below.

In the step~\ref{step:1}, un-selected PV panels are sorted  in a lexicographically  ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_{p}(Q_{n})$.
This sorting procedure gives a basic priority for all un-selected PV panels.
A panel with less ``$loss$'' and more modules for target current level are preferred.
The last sorting index $M_{p}(Q_{n})$ aim to minimize the number of selected PV modules for target current level, and it will be described in step~\ref{step:3}.
Moreover, according to equation~(\ref{eq:4}), the $Loss-rate$ is infinity for those PV panels who have no active modules.

In the step~\ref{step:2}, sorted PV panels are selected one by one until reaching $m$, the required number of active modules per-string.

In the step~\ref{step:3}, the number of active PV modules and the number of selected panels are optimized.

\section{Evaluation}\label{sec:evaluation}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.
